Case for Support

### 2021-11-10 caseForSupport.tex
Section 1 Background to the resource completed

\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{natbib}
\usepackage{apalike}
\usepackage{graphicx}

@@

\section{Background to the Resource}

@@

A central goal of the software development proposed here is to address this
problem, by providing Bonsai~(an experimental control software ecosystem;
Figure~\ref{fig:bonsai} and Section~\ref{sec:bonsai}) with state-of-the-art online (and offline) data
analysis methods (Figure~\ref{fig:proposedBonsaiExtensions} and 
Section~\ref{sec:toBeAddedMachineIntelligenceFunctionality}).
%
It is unfortunate that neuroscientists currently do not have software that
allows them to easily compare the performance of different data analysis
methods for the characterization of their datasets. The second central goal
of this proposal is to address this limitation by adding to Bonsai a generic
mechanism for comparing the performance of different methods for the analysis
of specific datasets (Section~\ref{sec:comparisonOfMultipleMethods}).

@@

@@

\section{Details of Resource}

\subsection{Video-based behavioral analysis}
\label{sec:videoBasedBehavioralAnalysis}

@@

\subsection{Spike sorting}
\label{sec:spikeSorting}

@@

\subsection{Low-dimensional representations of spiking data}
\label{sec:lowDimensionalRepresentationsOfSpikingData}

@@

\subsection{Low-dimensional representations of local-field potentials}
\label{sec:lowDimensionalRepresentationsOfLFPs}

@@

\subsection{Neural decoding}
\label{sec:neuralDecoding}

@@

\subsection{Comparing multiple data-analysis methods}
\label{sec:comparisonOfMultipleMethods}

@@

\section{Community Demand}

>>>>

\usepackage[colorlinks=true]{hyperref}
\usepackage{natbib}
\usepackage{apalike}
\usepackage{graphicx}

@@

\section{Background to the resource}

@@

A central goal of the software resource proposed here is to address this
problem, by providing Bonsai~(an experimental control software ecosystem;
Figure~\ref{fig:bonsai} and Section~\ref{sec:bonsai}) with state-of-the-art
online (and offline) data analysis methods
(Figure~\ref{fig:proposedBonsaiExtensions} and
Section~\ref{sec:toBeAddedMachineIntelligenceFunctionality}). Bonsai is
\textbf{unique} among experimental control software in that it allows people
with no programming experience to control sophisticated experiments. With the
proposed functionality to be added to Bonsai, its users will be able to use
sophisticated machine-learning methods to control their experiments and analyze
their data. This popularization of machine learning functionality will allow
scientists without computational skills to control sophisticated experiments
and analyze their data in unprecedented ways, which will most probably yield
important \textbf{advances in science}.

@@

Using the proposed Bonsai capabilities to communicate with software written in
other languages, we will integrate into Bonsai an initial set of state-of-the
art data analysis methods
(Section~\ref{sec:toBeAddedMachineIntelligenceFunctionality}). Developers of
advanced data-analysis methods should become interested in integrating their
algorithm into de Bonsai ecosystem because, which will allow their methods to
reach the wide Bonsai community. In addition this integration will enable
method developers, to easily compare the performance of of their methods with
that of other methods integrated into the Bonsai ecosystem. Method developers
witll become a new type of Bonsai users. These new users, will contribute to
the \textbf{sustainability} of the proposed resource beyond the period of
BBSRC-BBR funding.

@@

\section{Details of resource}

\subsection{Machine intelligence functionality to be added to Bonsai}
\label{sec:toBeAddedMachineIntelligenceFunctionality}

\subsubsection{Video-based behavioral analysis}
\label{sec:videoBasedBehavioralAnalysis}

@@

\subsubsection{Spike sorting}
\label{sec:spikeSorting}

@@

\subsubsection{Low-dimensional representations of spiking data}
\label{sec:lowDimensionalRepresentationsOfSpikingData}

@@

\subsubsection{Low-dimensional representations of local-field potentials}
\label{sec:lowDimensionalRepresentationsOfLFPs}

@@

\subsubsection{Neural decoding}
\label{sec:neuralDecoding}

@@

\subsubsection{Comparing multiple data-analysis methods}
\label{sec:comparisonOfMultipleMethods}

@@

\section{Community demand}
